---
title: "Project Markdown"
output: html_document
---

# One Time Papaja Installation
Below is the code used to install tinytex in order to install papaja.

```{r}

if(!requireNamespace("tinytex", quietly = TRUE)) install.packages("tinytex")
tinytex::install_tinytex()

```

After installing tinytex, we are now able to install papaja as seen below. These two 
chunks of code are only for one time use.

```{r}
# Install latest CRAN release
install.packages("papaja")

# Install remotes package if necessary
if(!requireNamespace("remotes", quietly = TRUE)) install.packages("remotes")

# Install the stable development version from GitHub
remotes::install_github("crsh/papaja")

# Install the latest development snapshot from GitHub
remotes::install_github("crsh/papaja@devel")

```

# Libraries
The below two lines of code open the libraries that are necessary for the analysis of this data. 

```{r}
library("tidyverse")
library(gridExtra)
```

# Bitcoin Data Refinement
The following code checks if a refined version of the Bitcoin data exists in a CSV file. If it doesn't exist, the original Bitcoin data is read in and then refined by removing unnecessary columns, creating a new column called "Trading Days since ICO", dropping any rows with missing data, and renaming columns. The refined data is then written to a new CSV file called "Bitcoin_refined.csv". If the refined data already exists in the CSV file, it is simply read in from the file.

```{r}

if (!file.exists("archive/Bitcoin_refined.csv")) {
  # read in original data
  Bitcoin <- read.csv("archive/Bitcoin.csv")
  
  # refine data
  Bitcoin_refined <- Bitcoin %>% 
    select(-Open, -High, -Low, -Close) %>% 
    mutate(`Trading Days since ICO` = row_number()) %>% 
    drop_na() %>% 
    rename(Date = 1, 
           `Trading Volume` = 2, 
           `Market Cap` = 3, 
           `Trading Days since ICO` = 4)
  
  # write refined data to CSV
  write_csv(Bitcoin_refined, "archive/Bitcoin_refined.csv")
  
} else {
  # read in refined data from CSV
  Bitcoin_refined <- read_csv("archive/Bitcoin_refined.csv")
}

```

# Bitcoin Graphs
The following code creates two graphs using the refined Bitcoin data: one displaying the Bitcoin trading volume by day and the other displaying the Bitcoin market cap by day. The grid.arrange() function arranges the two graphs side by side.
```{r}

#Bitcoin Graphs:
p1 <- ggplot(Bitcoin_refined, aes(`Trading Days since ICO`, `Trading Volume`)) + 
  geom_path() + ggtitle("Bitcoin Trading Volume by Day")

p2 <- ggplot(Bitcoin_refined, aes(`Trading Days since ICO`, `Market Cap`)) + 
  geom_path() + ggtitle("Bitcoin Market Cap by Day")

grid.arrange(p1, p2, ncol = 2)

```

# Ethereum Data Refinement
The following code checks if a refined version of the Ethereum data exists in a CSV file. If it doesn't exist, the original Ethereum data is read in and then refined by removing unnecessary columns, creating a new column called "Trading Days since ICO", dropping any rows with missing data, and renaming columns. The refined data is then written to a new CSV file called "Ethereum_refined.csv". If the refined data already exists in the CSV file, it is simply read in from the file.
```{r}

if (!file.exists("archive/Ethereum_refined.csv")) {
  # read in original data
  Ethereum <- read.csv("archive/Ethereum.csv")
  
  # refine data
  Ethereum_refined <- Ethereum %>% 
    select(-Open, -High, -Low, -Close) %>% 
    mutate(`Trading Days since ICO` = row_number()) %>% 
    drop_na() %>% 
    rename(Date = 1, 
           `Trading Volume` = 2, 
           `Market Cap` = 3, 
           `Trading Days since ICO` = 4)
  
  # write refined data to CSV
  write_csv(Ethereum_refined, "archive/Ethereum_refined.csv")
  
} else {
  # read in refined data from CSV
  Ethereum_refined <- read_csv("archive/Ethereum_refined.csv")
}

```

# Ethereum Graphs
The following code creates two graphs using the refined Ethereum data: one displaying the Ethereum trading volume by day and the other displaying the Ethereum market cap by day. The grid.arrange() function arranges the two graphs side by side.
```{r}

#Ethereum Graphs:
p1 <- ggplot(Ethereum_refined, aes(`Trading Days since ICO`, `Trading Volume`)) + 
  geom_path() + ggtitle("Ethereum Trading Volume by Day")

p2 <- ggplot(Ethereum_refined, aes(`Trading Days since ICO`, `Market Cap`)) + 
  geom_path() + ggtitle("Ethereum Market Cap by Day")

grid.arrange(p1, p2, ncol = 2)

```

# Dogecoin Data Refinement
The following code checks if a refined version of the Dogecoin data exists in a CSV file. If it doesn't exist, the original Dogecoin data is read in and then refined by removing unnecessary columns, creating a new column called "Trading Days since ICO", dropping any rows with missing data, and renaming columns. The refined data is then written to a new CSV file called "Dogecoin_refined.csv". If the refined data already exists in the CSV file, it is simply read in from the file.
```{r}

if (!file.exists("archive/Dogecoin_refined.csv")) {
  # read in original data
  Dogecoin <- read.csv("archive/Dogecoin.csv")
  
  # refine data
  Dogecoin_refined <- Dogecoin %>% 
    select(-Open, -High, -Low, -Close) %>% 
    mutate(`Trading Days since ICO` = row_number()) %>% 
    drop_na() %>% 
    rename(Date = 1, 
           `Trading Volume` = 2, 
           `Market Cap` = 3, 
           `Trading Days since ICO` = 4)
  
  # write refined data to CSV
  write_csv(Dogecoin_refined, "archive/Dogecoin_refined.csv")
  
} else {
  # read in refined data from CSV
  Dogecoin_refined <- read_csv("archive/Dogecoin_refined.csv")
}

```

# Dogecoin Graphs
The following code creates two graphs using the refined Dogecoin data: one displaying the Dogecoin trading volume by day and the other displaying the Dogecoin market cap by day. The grid.arrange() function arranges the two graphs side by side.
```{r}

#Dogecoin Graphs:
p1 <- ggplot(Dogecoin_refined, aes(`Trading Days since ICO`, `Trading Volume`)) + 
  geom_path() + ggtitle("Dogecoin Trading Volume by Day")

p2 <- ggplot(Dogecoin_refined, aes(`Trading Days since ICO`, `Market Cap`)) + 
  geom_path() + ggtitle("Dogecoin Market Cap by Day")

grid.arrange(p1, p2, ncol = 2)

```

# Shiba INU Data Refinement
The following code checks if a refined version of the Shiba INU data exists in a CSV file. If it doesn't exist, the original Shiba INU data is read in and then refined by removing unnecessary columns, creating a new column called "Trading Days since ICO", dropping any rows with missing data, and renaming columns. The refined data is then written to a new CSV file called "Shiba INU_refined.csv". If the refined data already exists in the CSV file, it is simply read in from the file.
```{r}

if (!file.exists("archive/Shiba INU_refined.csv")) {
  # read in original data
  `Shiba INU` <- read.csv("archive/Shiba INU.csv")
  
  # refine data
  `Shiba INU_refined` <- `Shiba INU` %>% 
    select(-Open, -High, -Low, -Close) %>% 
    mutate(`Trading Days since ICO` = row_number()) %>% 
    drop_na() %>% 
    rename(Date = 1, 
           `Trading Volume` = 2, 
           `Market Cap` = 3, 
           `Trading Days since ICO` = 4)
  
  # write refined data to CSV
  write_csv(`Shiba INU_refined`, "archive/Shiba INU_refined.csv")
  
} else {
  # read in refined data from CSV
  `Shiba INU_refined` <- read_csv("archive/Shiba INU_refined.csv")
}

```

# Shiba INU Graphs
The following code creates two graphs using the refined Shiba INU data: one displaying the Shiba INU trading volume by day and the other displaying the Shiba INU market cap by day. The grid.arrange() function arranges the two graphs side by side.
```{r}

#Shiba INU Graphs:
p1 <- ggplot(`Shiba INU_refined`, aes(`Trading Days since ICO`, `Trading Volume`)) + 
  geom_path() + ggtitle("Shiba INU Trading Volume by Day")

p2 <- ggplot(`Shiba INU_refined`, aes(`Trading Days since ICO`, `Market Cap`)) + 
  geom_path() + ggtitle("Shiba INU Market Cap by Day")

grid.arrange(p1, p2, ncol = 2)

```

